The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2016-09-13 paper/ms.tex
Minor paper edits

\begin{abstract}
We present the first release of the ``Galaxy Cluster Merger Catalog''. This catalog provides an extensive suite of mock observations and related data for N-body and hydrodynamical simulations of galaxy cluster mergers. These mock observations consist of projections of a number of important observable quantities in several different wavebands, for the entire evolution of each simulation as well as along different lines of sight through the three-dimensional simulation domain. The web interface to the catalog consists of easily browseable images over epoch and projection direction, as well as download links for the raw data and a JS9 interface for interactive data exploration. All of the data products are provided in the standard FITS file format, in image and table form. Data is being stored on the yt Hub~(\url{https://hub.yt}), which allows for remote access and analysis using Jupyter notebook server. Future versions of the catalog will include simulations from a number of research groups and a variety of research topics related to the study of interactions of galaxy clusters with each other and with their member galaxies. The catalog is located at \url{http://gcmc.hub.yt}.
\end{abstract}

@@

The projected data is generated from the original simulation data using yt \citep{tur11}, an open-source Python package for analyzing and visualizing volumetric data. yt has capabilities for slicing and projecting physical fields from multi-resolution datasets such as those from galaxy cluster merger simulations along arbitrary lines of sight. Through analysis modules and affiliated packages, yt also has capabilities to produce synthetic Sunyaev-Zeldovich (S-Z) and X-ray observations. We provide details on how this is done in Sections \ref{sec:sz} and \ref{sec:xray}.

AstroPy \citep{apy13} is used to take the projected data generated in yt and produce data outputs in the standard Flexible Image Transport System (FITS) data format \citep{pen10} and generate coordinates for the files using the World Coordinate System \citep[WCS,][]{gre02, cal02} specification.

>>>>

\begin{abstract}
We present the first release of the ``Galaxy Cluster Merger Catalog''. This catalog provides an extensive suite of mock observations and related data for N-body and hydrodynamical simulations of galaxy cluster mergers. These mock observations consist of projections of a number of important observable quantities in several different wavebands, for the entire evolution of each simulation as well as along different lines of sight through the three-dimensional simulation domain. The web interface to the catalog consists of easily browseable images over epoch and projection direction, as well as download links for the raw data and a JS9 interface for interactive data exploration. All of the data products are provided in the standard FITS file format, in image and table form. Data is being stored on the yt Hub~(\url{http://hub.yt}), which allows for remote access and analysis using a Jupyter notebook server. Future versions of the catalog will include simulations from a number of research groups and a variety of research topics related to the study of interactions of galaxy clusters with each other and with their member galaxies. The catalog is located at \url{http://gcmc.hub.yt}.
\end{abstract}

@@

The projected data is generated from the original simulation data using \code{yt} \citep{tur11}, an open-source Python package for analyzing and visualizing volumetric data. \code{yt} has capabilities for slicing and projecting physical fields from multi-resolution datasets such as those from galaxy cluster merger simulations along arbitrary lines of sight. Through analysis modules and affiliated packages, \code{yt} also has capabilities to produce synthetic Sunyaev-Zeldovich (S-Z) and X-ray observations. We provide details on how this is done in Sections \ref{sec:sz} and \ref{sec:xray}.

\code{AstroPy} \citep{apy13} is used to take the projected data generated in \code{yt} and produce data outputs in the standard Flexible Image Transport System (FITS) data format \citep{pen10} and generate coordinates for the files using the World Coordinate System \citep[WCS,][]{gre02, cal02} specification.
